MADA Data Analysis Project

### 2021-10-29 products/Part_2/DataExploration.Rmd
10 basics push - Work in prog
Basic push to not lose any data before refining and removing excess parts.

MC

__Making the UndeterminedData__
see above but added filter() for Ct=="Undetermined" to pull all data with Undetermined as a reported value

@@

####Run summaries

####Exploritory Figures

@@

![resultfigure2](../../results/resultfigure2.png)
Interesting-- why is there such a group difference in Surface Sampling experiements versus Spike
Oh makes sense it's SD- the serial dilution. We expect the SD to be like the standard curve and the recovery should have loss.

@@

>>>>

__Making the UndeterminedData__

see above but added filter() for Ct=="Undetermined" to pull all data with Undetermined as a reported value

@@

#### Run summaries

#### Exploritory Figures

@@

![resultfigure2](../../results/resultfigure2.png)
Interesting-- why is there such a group difference in Surface Sampling experiments versus Spike
Oh makes sense it's SD- the serial dilution. We expect the SD to be like the standard curve and the recovery should have loss.

@@

##### Local Polynomial Regression Smoothing (loess) with polynomial formula

![SS300-Smooth](../../results/SS300Smooth.png)

##### Density Plots -Experimental view

###### Desnsity Output

Doesn't take into account for the replicates in Sample facet. SD facet seems more in line.
![SS300-Density](../../results/SS300-Density.png)

###### ECDF analysis - Look into the data this way to see if __HOW__ different these are

This is an ECDF between the Phase 2 runs. This compares CDC ONLY data between the two PCR runs as we adjusted changes. Done so I can include the CDC data with little change in code.
Appears to have little difference, likely insignifant- will need to run stats.
![SS300-ECDF.PCR](../../results/SS300-ECDF.PCR.png)

###### 
Exploring the

![SS300-ECDF.Type](../../results/SS300-ECDF.Type.png)

![SS300-ECDF.Method](../../results/SS300-ECDF.Method.png)

### 2021-10-29 products/manuscript/Manuscript.Rmd
10 basics push - Work in prog
Basic push to not lose any data before refining and removing excess parts.

MC

The structure below is a possible setup for a data analysis project (including the course project). For a manuscript, adjust as needed.

@@

## General Background Information
_Provide enough background on your topic that others can understand the why and how of your analysis_

### Surfaces Preparation  
Stainless-steel coupons (10x20in) were triple washed with detergent, rinsed with RO water, sprayed with 70% Ethanol and left to air dry. The dry coupons were wrapped in craft paper and autoclaved on a solid cycle.  Before use, the coupons are unwrapped while in a BSC

### Inoculum Preparation
A serial dilution of heat-inactivated SARS-CoV-2 (~10^6 copies/uL, ATCC Strain) and Viral Transport Media (CDC protocol) was created

### Inoculation of Surfaces

## Description of data and data source
_Describe what the data is, what it contains, where it is from, etc. Eventually this might be part of a methods section._

Data was self recorded over several experimental runs of an on going series. 
The current set has 379 observations and 23 variables. Additional data will be added into this set as experiments are completed throughout the course.
The data itself is a combination of observed processing variables and the resulting RT-PCR data. Copy data may eventually be included. It is currently calculated in an excel document, but may be reproduced in this project for best practice).
A copy of the data has been placed in the data folder of this repository.

## Questions/Hypotheses to be addressed

@@

# Methods and Results

_In most research papers, results and methods are separate. You can combine them here if you find it easier. You are also welcome to structure things such that those are separate sections._

## Data aquisition
_As applicable, explain where and how you got the data. If you directly import the data from an online source, you can combine this section with the next._

## Data import and cleaning

Data comes out of different reports. This report is added to a supplemental report gathered while the samples were processed and added into one giant compilation then read into R.

>>>>

@@

##  Background
The global Coronavirus Disease 2019 (COVID-19) pandemic continues to persist due to the timing of an available vaccine, varying adherence to COVID-19 public health safety recommendations, and the emergence of SARS-CoV-2 (SC2) variants. Environmental reservoirs are a reported, indirect transmission route for viral pathogens. Although many viruses have a low infectious dose, they can be difficult to detect due to the low bioburden in the environment. The ability to detect viral pathogens is critical to identifying hidden reservoirs which can inform infection control. Culture-based methods can be labor and time intensive. The use and limitations of commercial “target capture” (TC) technologies are varied compared to molecular approaches utilizing automated extraction. The objective of this study is improve outbreak response through rapid pathogen detection by evaluating a TC technology’s ability to capture SC2 from complex matrices.

### Questions/Hypotheses to be addressed

@@

## Methods and Results

Using established standard methods for environmental sampling with a self-contained polyurethane swab, a TC approach (NTP; Nanotrap® Magnetic Virus Particles, Ceres Nanosciences) was compared to an automated extraction method (MX48; Maxwell® RSC Viral Total Nucleic Acid Purification Kit, Promega) for recovery of heat-inactivated SC2 from the polyurethane swab as detected by rRT-PCR

## Data aquisition
Reports per each rRT-PCR run were generated and quality checked on their respective machines before transfer to a Teams repository. Summary data was selected from the reports and added to additional environmental data gathered on based on the extraction date of the sample.
Completed run data is then collated into one file and red into R.

### Data import and cleaning
